Seminarium IN3130\\ Title goes here

### 2014-03-01 authorinstr_2.tex
Aanpassingen volgorde en kleine verbeteringen

\section{Tweet stream analysis}
\subsection{Statistics}
\subsection{user modeling}
\subsection{Classification}
\subsection{Tag based analysis}
\subsection{Event identification}
\subsubsection{What is Event Identification}
Event identification is the problem of identifying events(e.g. concerts, festivals \& incidents) in a twitter-stream. The events identified range from Worldwide to local events. Twitter-messages related to an event can be a useful source of information spreading information earlier than 'old' media.

To identify an event, a definition of an event is needed. \cite{eventident} defines an event as: "a real world occurence $e$ with (1) an associated Time Period $T_e$ and (2) a time-ordered stream of Twitter messages $M_e$, of substantial volume, discussing the
occurrence and published during time $T_e$."

\subsubsection{Event Identification Issues}

\textbf{Aligning Tweets with an Event} \\
On average thousands of tweets are sent using Twitter every minute. One of the main challenges in Event Identification is the alignment of tweets with their respective event. 
\\\\
\textbf{Separation of Event and Non-event Content}\\
Because not all tweets on twitter are event content, a seperation of Event and Non-event content is done prior of identifying events. To achieve this separation, \cite{eventident} uses an incremental clustering algorithm(ICA). ICA doesn't require an number of clusters before the execution of the algorithm. This is an useful feature in the constantly changing twitter-environment.

After the clustering a number of features is used to distinguish between event and non-event clusters. The following features are used by \cite{eventident} to identify an event cluster. 
\begin{itemize}
  \item Temporal: TODO
  \item Social: The interactions between users(e.g. retweets, replies \& mentions) during events could differ from other activities. 
  \item Topical: Tweets about events tend to center more around one central topic. Furthermore messages in event clusters are more likely to share one or more event-specific key-terms.  
  \item Twitter-centric: TODO
\end{itemize}
With this list of features a two event classifier is trained using two different techniques. The first classifier is trained using the "WEKA tookit"(TODO), in the second classifier the  Naive-Bayes technique is used. According to \cite{eventident} the first classifier outperforms the second classifier in the separation of event and non-event clusters. 
\section{Conclusion}

>>>>

\section{Tweet stream analysis}
\subsection{Statistics}
\subsection{user modeling}
\subsection{Classification}
\subsection{Tag based analysis}
\subsection{Event identification}
\subsubsection{What is Event Identification}
Event identification is the problem of identifying events(e.g. concerts, festivals \& incidents) in a twitter-stream. The events identified range from Worldwide to local events. Twitter-messages related to an event can be a useful source of information as they often spread news earlier than the 'old' media (e.g News Papers \& News Sites)

To identify an event using an algorithm, a definition of an event is needed. \cite{eventident} defines an event as: "a real world occurence $e$ with (1) an associated Time Period $T_e$ and (2) a time-ordered stream of Twitter messages $M_e$, of substantial volume, discussing the
occurrence and published during time $T_e$."

\subsubsection{Event Identification Issues}
In this section we will discuss several issues regarding Event Identification and the solutions associated with them.
\\\\ 
\textbf{Separation of Event and Non-event Content}\\
Because not all tweets on twitter are event content, a seperation of Event and Non-event content is done prior of identifying events. To achieve this separation, \cite{eventident} uses an incremental clustering algorithm(ICA). ICA doesn't require an number of clusters before the execution of the algorithm. This is an useful feature in the constantly changing twitter-environment.

After the clustering a number of features is used to distinguish between event and non-event clusters. The following features are used by \cite{eventident} to identify an event cluster. 
\begin{itemize}
  \item Temporal: TODO
  \item Social: The interactions between users(e.g. retweets, replies \& mentions) during events could differ from other activities. 
  \item Topical: Tweets about events tend to center more around one central topic. Furthermore messages in event clusters are more likely to share one or more event-specific key-terms.  
  \item Twitter-centric: TODO
\end{itemize}
With this list of features two event-classifiers are trained using two different techniques. The first classifier is trained using the "WEKA tookit"(TODO), in the second classifier the  Naive-Bayes technique is used. According to \cite{eventident} the first classifier outperforms the second classifier in the separation of event and non-event clusters. 
\\\\
\textbf{Aligning Tweets with an Event} \\
On average thousands of tweets are sent using Twitter(bron) every minute. One of the main challenges in Event Identification is the alignment of tweets with their respective event. \cite{eventalign} tries to create an automated mapping solution for this problem using semantics.

\section{Conclusion}
